Managing variability in software systems

### 2021-04-24 Paper.tex
add Introduction v1

\section{Introduction}
Here we are going to introduce the reader into the broad environment  
(1/2 page) JR

>>>>

\section{Introduction}
Building software systems which can adopt to changes from outside as well as within said system represents a vital goal to build software systems that last. When these goals are achieved the effort and therefore costs are reduced for maintenance, but also for further improvements and extension. \\\\
Therefore, a lot of companies design their software such as numerous variants exists, which allows customization to meet the requirements which are laid out by customers and stakeholders. One of the most used practices to achieve a variant-rich software system is software product line engineering (SPLE) which uses concept, processes, modeling techniques for features and function, design patters and respective tools to support the process.[5]\\\\
If one wants to design a system which is prepared for change, the focus should lie on developing components which have loose coupling and strong cohesion. So a module solves one simple task and is as independent as it can be. This leads to the least amount of unwanted side effects in other modules if one module is confronted with unpredicted variability.\\\\
We will try to provide a basic introduction how variability is managed in software systems by collection information from other studies which describe the key aspects of this vast field of research. In the first section we are providing some base knowledge acquired previous studies. After that we will lay out how one can identify the various sources of variability in software systems. After that we will bring up techniques and processes which have the purpose of modeling the variation in a software system. Last but not least we will discuss some of the big tasks which have to be addressed and boil down the described aspects in this paper to a conclussion.
(1/2 page) JR
